Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-01 paper/main.tex
Trim subsections and contrast headings more
TODO for half-addressed issue

\subsection{Event modeling}

@@

\subsubsection{Events related to high-level perception} \label{rationale}

\todo[inline]{imo the subheadings for 2.6.1 and 2.6.2 can be dropped because
2.6.2 is super short}

@@

\subsubsection{Events related to low-level perception / low-level perceptual
confounds}

@@

\todo[inline]{SE: Die Abkürzungen in Figure 1: Da steigt keiner hinter}

\begin{figure*}[h!]
\centering
    \includegraphics[width=\linewidth]{figures/regressor-corr} \caption{Pearson
        correlation coefficients of the regressors used in the analysis of the
        audio-description (blue; see Table \ref{tab:ao-events} for a
        description) and audio-visual movie (red; see Table \ref{tab:av-events})
        rounded to the nearest tenth.
        The correlation between the two stimuli's
        root mean square loudness and between their left-right difference in
        loudness yielded the highest correlation values
        (\texttt{fg\_ad\_rms} and \texttt{fg\_av\_ger\_rms}, r=.7635;
        \texttt{fg\_ad\_lrdiff} and \texttt{fg\_av\_ger\_lrdiff}, r=.7749).}
\label{fig:reg-corr}
\end{figure*}

>>>>

\subsection{Event selection}

@@

@@

@@

\begin{figure*}[h!]
\centering
    \includegraphics[width=\linewidth]{figures/regressor-corr} \caption{Pearson
        correlation coefficients of the regressors used in the analysis of the
        audio-description (blue; see Table \ref{tab:ao-events} for a
        description) and audio-visual movie (red; see Table \ref{tab:av-events})
        rounded to the nearest tenth.
        The correlation between the two stimuli's
        root mean square loudness and between their left-right difference in
        loudness yielded the highest correlation values
        (\texttt{fg\_ad\_rms} and \texttt{fg\_av\_ger\_rms}, r=.7635;
        \texttt{fg\_ad\_lrdiff} and \texttt{fg\_av\_ger\_lrdiff}, r=.7749).
        \todo[inline]{not all labels are actually listed in that table}
      }
\label{fig:reg-corr}
\end{figure*}
